### 2017-02-13 section/5_exper.tex
fix comments from Shan

%\input section/tab_top5
{\color{red}
To answer \textbf{RQ2}, we apply
statistical performance debugging \cite{SongOOPSLA2014} to all our benchmarks
and apply \Tool to the top 5 ranked loops\footnote{Some extracted benchmarks
have fewer than 5 loops. We simply apply \Tool to all loops in these cases.}
to see how accurate \Tool is. 
}
{\color{red}
As shown in Table \ref{tab:benchmarks}, \Tool is accurate, having 2 real
false positive and 20 benign false positives in total for all the top five loops
of the \allbugs benchmarks.

@@

The two real false positives happen for benchmarks XXX and XXX.
These two loops are identified as
redundant and resultless by \Tool. However, they
are very difficult to fix and hence are not changed in the patches.
Since these two loops are ranked higher than the true positive loops by
statistical debugging, they could cost (waste) \Tool users some effort during 
performance diagnosis. Future work could try to prune these false positives
by estimating the fix difficulty.

\Tool also reports 20 benign false positives.
In these cases, \Tool correctly identified truly inefficient loops.
However, these loops are not the main contributors to the 
performance problems perceived by the users, and hence are not
fixed in patches. 
Different from the two false positives discussed above, these 20 loops are
ranked {\bf lower} than the true positive loops by statistical debugging, as
well as by profillers,
because of their low contributions to the perceived performance problems.
Consequently, they will not cause extra diagnosis effort for \Tool users.
}

@@

\noindent\textbf{Resultful and redundancy rate}
Our default setting should work in most cases.
In fact, the diagnosis results are largely {\bf in}sensitive to the threshold
setting. For example, the results would remain the same when
changing the redundancy rate threshold from 0.5 to any value between about
0.1 and 0.66. We will have 1 more false negative and 1 fewer benign false positive, 
when the rate is 0.7. The trend is similar for resultless loop checking. 
Developers can adjust these thresholds. 
They can even get rid of thresholds, and only
use the raw values of resultful/redundancy rates to understand
the absolute and relative (in)efficiency nature of suspicious 
loops. Based on our experiments, the difference between efficient and inefficient
loops is obvious based on these rates.

>>>>

%\input section/tab_top5
{\color{red}
To answer \textbf{RQ2}, we apply
statistical performance debugging \cite{SongOOPSLA2014} to all our benchmarks
and apply \Tool to the top 5 ranked loops\footnote{Some extracted benchmarks
have fewer than 5 loops. We simply apply \Tool to all loops in these cases.}
to see how accurate \Tool is. 
}
{\color{red}
As shown in Table \ref{tab:benchmarks}, \Tool is accurate, having five real
false positives and 17 benign false positives in total for all the top five loops
of the \allbugs benchmarks.

@@

The five real false positives happen for benchmarks GCC\#8805 and GCC\#12322.
These five loops are identified as
redundant and resultless by \Tool. However, they
are very difficult to fix and hence are not changed in the patches.
Since these five loops are ranked higher than the true positive loops by
statistical debugging, they could cost (waste) \Tool users some effort during 
performance diagnosis. Future work could try to prune these false positives
by estimating the fix difficulty.

\Tool also reports 17 benign false positives.
In these cases, \Tool correctly identified truly inefficient loops.
However, these loops are not the main contributors to the 
performance problems perceived by the users, and hence are not
fixed in patches. 
Different from the five false positives discussed above, these 17 loops are
ranked {\bf lower} than the true positive loops by statistical debugging, as
well as by profillers,
because of their low contributions to the perceived performance problems.
Consequently, they will not cause extra diagnosis effort for \Tool users.
}

@@

\noindent\textbf{Resultful and redundancy rate}
Our default setting should work in most cases.
In fact, the diagnosis results are largely {\bf in}sensitive to the threshold
setting. For example, the results would remain the same when
changing the redundancy rate threshold from 0.5 to any value between about
0.1 and 0.66. We will have 1 more false negative and 1 fewer true false positive, 
when the rate is 0.7. The trend is similar for resultless loop checking. 
Developers can adjust these thresholds. 
They can even get rid of thresholds, and only
use the raw values of resultful/redundancy rates to understand
the absolute and relative (in)efficiency nature of suspicious 
loops. Based on our experiments, the difference between efficient and inefficient
loops is obvious based on these rates.

### 2017-02-13 section/7_con.tex
fix comments from Shan

>>>>

\section*{Acknowledgment}
We thank the anonymous reviewers, Darko Marinov, and Ben Liblit for their comments.
Our research has been supported by NSF (CNS-1563956, IIS-1546543, CNS-1514256, CCF-1514189, CCF-1439091), 
and generous supports from Alfred P. Sloan Foundation and CERES Center for Unstoppable Computing.
